Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-06-10 papers/data_paper/datapaper.tex
arcetri wed

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3377.
  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3384.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3384}
  \end{table}

  The morphology of NGC3377 is similar to NGC0821. 
  The unsharp mask reveals an embedded disc and the extended velocity field confirms that 
  it is not a large-scale disc. 
  The residual image from a 2D single S\'ersic fit diplays the unsubtracted embedded disc
  and an additional nuclear ($\lesssim 10''$) component.
  The embedded disc is very close to edge-on.
  In the 2D fit we adopt a S\'ersic + edge-on disc model, after masking the third nuclear component. 
  In the 1D fit we are not able to model the embedded disc with an exponential function, 
  probably because of the orientation of the disc. 
  The best results are obtained when a Ferrer function is employed. 
  We tried to model the nuclear cusp with a PSF or a gaussian function. The gaussian function parameters
  resulted highly degenerate with the Ferrer function parameters, leading us to prefer a PSF profile. \\

>>>>

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3377.
  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
  For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
  with a disk-to-bulge transition occurring at about $R_{\rm maj} \sim 50''$.
  \citet{arnold2014} attempted a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile 
  rather than a three-parameter $R^{1/n}$ S\'ersic function.
  Here we use a surface brightness profile twice as extended as that used by \citet{arnold2014} 
  and we identify a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component.
  The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
  and also from the ellipticity profile, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
  and then drops at larger radii.
  The nuclear stellar disk can be spotted from the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
  Each of the two disks is modelled with an exponential profile. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3377}
  \end{table}
